---
title: "Analysis for the 'Hidden Attitudes' paper"
author: "Daiki Hiramori and Kairi Shimabukuro"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
    pdf_document:
        latex_engine: xelatex
geometry: margin = 1in
mainfont: Times New Roman
fontsize: 11pt
header-includes:
  - \usepackage{xltxtra}
  - \usepackage{zxjatype}
  - \usepackage[hiragino-pron]{zxjafont}
---

R code for a paper tentatively titled “Hidden Attitudes? Reassessing Support for Same-Sex Marriage in Japan through a List Experiment”

# Initial Data Analysis

```{r}
#penalize excessive significant figures
options(digits = 3)

#prevent scientific notation
options(scipen = 10)

#packages used in this analysis
library(tidyverse)
```

```{r}
#import raw data
data <- read_csv("data/rawdata.csv", locale = locale(encoding = "CP932"), show_col_types = FALSE)
```

```{r}
#recode variables
#treatment group vs. control group
table(data$cellname)
table(data$cid)

data <- data %>%
  mutate(group = case_when(
    cid >= 1  & cid <= 10 ~ 1,
    cid >= 11 & cid <= 20 ~ 2,
    TRUE ~ NA_real_
  ))

#direct question
table(data$q10)
data <- data %>%
  mutate(direct = recode(q10,
                         `1` = 1,
                         `2` = 0,
                         .default = NA_real_))
table(data$q10, data$direct)

#rename group
data <- data %>%
  mutate(group = factor(group,
                        levels = c(1, 2),
                        labels = c("treatment", "control")))

round(prop.table(table(data$cid, data$group), margin = 1) * 100, 1)

#delete satisficers
data <- data %>%
  filter(q7_5 == 2)
```

```{r}
#compare the means of the selected items

data %>%
  group_by(group) %>%
  summarise(
    mean = mean(q9_1fa, na.rm = TRUE),
    sd = sd(q9_1fa, na.rm = TRUE),
    n = n()
    )

diff <- data %>%
  group_by(group) %>%
  summarise(mean = mean(q9_1fa, na.rm = TRUE)) %>%
  pivot_wider(names_from = group, values_from = mean) %>%
  mutate(diff = (`treatment` - `control`) * 100)
diff <- diff[[3]]
```

結果1：5問群（実験群）と4問群（統制群）の差から計算した「実際の」同性婚賛成割合は、`r round(diff, 3)`% である。

```{r}
avr <- data %>%
  group_by(group) %>%
  summarise(mean_direct = mean(direct, na.rm = TRUE)*100)
pull(avr)

average <- avr[[2, 2]]
```

結果2：リスト実験で同性婚賛否の設問を見なかった4問群（統制群）において、直接同性婚の賛否を聞いた場合の同性婚賛成割合は`r round(average, 3)`%である。

**結果3：直接聞いた場合と間接的に聞いた場合では、`r round(average-diff, 3)`%差がある（実際よりも賛成割合が過大推定されている）。**