---
title: "Analysis for the 'Hidden Attitudes' paper"
author: "Daiki Hiramori and Kairi Shimabukuro"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
    pdf_document:
        latex_engine: xelatex
geometry: margin = 1in
mainfont: Times New Roman
fontsize: 11pt
header-includes:
  - \usepackage{xltxtra}
  - \usepackage{zxjatype}
  - \usepackage[hiragino-pron]{zxjafont}
---

R code for a paper tentatively titled “Hidden Attitudes? Reassessing Support for Same-Sex Marriage in Japan through a List Experiment”

# Initial Data Analysis

```{r}
#penalize excessive significant figures
options(digits = 3)

#prevent scientific notation
options(scipen = 10)

#packages used in this analysis
library(tidyverse)
```

```{r}
#import raw data
data <- read_csv("data/rawdata.csv", locale = locale(encoding = "CP932"),
                 show_col_types = FALSE)
```

```{r}
#recode variables
#treatment group vs. control group
table(data$cellname)
table(data$cid)

data <- data %>%
  mutate(group = case_when(
    cid >= 1  & cid <= 10 ~ 1,
    cid >= 11 & cid <= 20 ~ 2,
    TRUE ~ NA_real_
  ))

#direct question
table(data$q10)
data <- data %>%
  mutate(direct = recode(q10,
                         `1` = 1,
                         `2` = 0,
                         .default = NA_real_))
table(data$q10, data$direct)

#rename group
data <- data %>%
  mutate(group = factor(group,
                        levels = c(1, 2),
                        labels = c("treatment", "control")))

round(prop.table(table(data$cid, data$group), margin = 1) * 100, 1)

#delete satisficers
table(data$q7_5)
100*prop.table(table(data$q7_5))

data <- data %>%
  filter(q7_5 == 2)
```

```{r}
#compare the means of the selected items

data %>%
  group_by(group) %>%
  summarise(
    mean = mean(q9_1fa, na.rm = TRUE),
    sd = sd(q9_1fa, na.rm = TRUE),
    n = n()
    )

diff <- data %>%
  group_by(group) %>%
  summarise(mean = mean(q9_1fa, na.rm = TRUE)) %>%
  pivot_wider(names_from = group, values_from = mean) %>%
  mutate(diff = (`treatment` - `control`) * 100)
diff <- diff[[3]]
```

結果1：5問群（実験群）と4問群（統制群）の差から計算した「実際の」同性婚賛成割合は、`r round(diff, 3)`% である。

```{r}
avr <- data %>%
  group_by(group) %>%
  summarise(mean_direct = mean(direct, na.rm = TRUE)*100)
pull(avr)

average <- avr[[2, 2]]
```

結果2：リスト実験で同性婚賛否の設問を見なかった4問群（統制群）において、直接同性婚の賛否を聞いた場合の同性婚賛成割合は`r round(average, 3)`%である。

**結果3：直接聞いた場合と間接的に聞いた場合では、`r round(average-diff, 3)`%差がある（実際よりも賛成割合が過大推定されている）。**

# Main Data Analysis

```{r}
#packages used in this analysis
library(list)

#recode the group variable
data <- data %>%
  mutate(treat = case_when(
    group == "control" ~ 0,
    group == "treatment" ~ 1
  ))

#convert the format
data <- as.data.frame(data)
```

```{r}
# Direct question estimate
data <- data %>%
  mutate(direct_support = case_when(
    q10 == 1 ~ 1, 
    q10 == 2 ~ 0,   
    TRUE ~ NA_real_
  ))

direct_est <- mean(data$direct_support, na.rm = TRUE)
direct_n   <- sum(!is.na(data$direct_support))
direct_se  <- sqrt(direct_est * (1 - direct_est) / direct_n)

cat("Direct estimate:", round(direct_est, 4), 
    "SE:", round(direct_se, 4), 
    "N:", direct_n, "\n")
```

```{r}
# Check No Design Effects Assumption
ict.test(y = data$q9_1fa, treat = data$treat, J = 4)

# Check Ceiling and Floor Effects
table(data$q9_1fa[data$treat == 0])
100*prop.table(table(data$q9_1fa[data$treat == 0]) )
table(data$q9_1fa[data$treat == 1])
100*prop.table(table(data$q9_1fa[data$treat == 1]))

nls_fit <- ictreg(q9_1fa ~ 1, data = data, treat = "treat", J = 4, method = "nls")
summary(nls_fit)
```

```{r}
# Calculate list experiment difference in means
diff.in.means.results <- ictreg(q9_1fa ~ 1, data = data, 
                  treat = "treat", J=4, method = "lm")

summary(diff.in.means.results)
```

```{r}
# Setup: fit base models on full sample
fit.list <- ictreg(q9_1fa ~ q5 + AGE + q4 + q8, data = data, 
                    treat = "treat", J = 4, method = "ml")

fit.ceiling <- ictreg(q9_1fa ~ q5 + AGE + q4 + q8, data = data, 
                    treat = "treat", J = 4, method = "ml", ceiling = TRUE)

fit.sens <- glm(direct_support ~ q5 + AGE + q4 + q8, 
                 data = data %>% filter(treat == 0), 
                 family = binomial("logit"))

# Gender subgroups
data <- data %>%
  mutate(gender = case_when(
    q5 == 1 ~ "Men",
    q5 == 2 ~ "Women",
    q5 == 3 ~ "Non-binary"
  ))

for (grp in c("Men", "Women", "Non-binary")) {
  cat(grp)
  print(predict(fit.list, direct.glm = fit.sens,
        newdata = data %>% filter(gender == grp),
        newdata.direct = data %>% filter(treat == 0, gender == grp),
        se.fit = TRUE, avg = TRUE))
}

# Age subgroups
data <- data %>%
  mutate(age_group = case_when(
    AGE < 40 ~ "Younger",
    AGE >= 40 & AGE < 60 ~ "Middle",
    AGE >= 60 & AGE < 70 ~ "Older"
  ))

for (grp in c("Younger", "Middle", "Older")) {
  cat(grp)
  print(predict(fit.list, direct.glm = fit.sens,
        newdata = data %>% filter(age_group == grp),
        newdata.direct = data %>% filter(treat == 0, age_group == grp),
        se.fit = TRUE, avg = TRUE))
}

#Education subgroups
data <- data %>%
  mutate(edu = case_when(
    q4 <= 2 ~ "HS or less",
    q4 >= 3 ~ "Higher ed"
  ))

for (grp in c("HS or less", "Higher ed")) {
  cat(grp)
  print(predict(fit.list, direct.glm = fit.sens,
        newdata = data %>% filter(edu == grp),
        newdata.direct = data %>% filter(treat == 0, edu == grp),
        se.fit = TRUE, avg = TRUE))
}

# Political ideology subgroups
data <- data %>%
  mutate(political = case_when(
    q8 <= 3 ~ "Liberal",
    q8 == 4 ~ "Center",
    q8 >= 5 ~ "Conservative"
  ))

for (grp in c("Liberal", "Center", "Conservative")) {
  cat(grp)
  print(predict(fit.list, direct.glm = fit.sens,
        newdata = data %>% filter(political == grp),
        newdata.direct = data %>% filter(treat == 0, political == grp),
        se.fit = TRUE, avg = TRUE))
}
```

